Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
pass

Considering severity levels, it is worth noting that \jsc{}~\cite{jsc-severity} 
and \smonkey{}~\cite{mozilla-severity} uses five levels, 
whereas \chakra{}~\cite{chakra-severity} and \veight{}~\cite{v8-severity} 
use only three. As usual, the smallest the severity value the 
highest the severity of the bug. We use a dash (``-'') 
in place of the severity level for the cases where the bug 
report is pending confirmation.\Mar{por favor,
  corrija estes numeros *com cuidado*! se possivel, use macros.} Of
the \Fix{17} bugs we reported in this experiment, \Fix{9} were
promoted from the status ``New'' to ``Confirmed''. Of these, \Fix{8}
are severity-2 bugs.  Although we did not find any showstopper
critical bugs, most of the bugs are seemingly important as per the
categorization given by engineers. Analyzing the issue tracker of
\chakra, we found that severity-1 bugs are indeed rare. Considering
the bugs confirmed by developers, \chakra{} was the engine with the
highest number, \Fix{8} in total, with \Fix{1} bug fixed. Considering
the remaining engines, \veight{} developers confirmed \Fix{two} of the
\Fix{three} bug we reported, fixing \Fix{one}. Curiously, Google
engineers confirmed the report we issued in a few hours. We found that
development teams of other engines, specially \jsc\, took much longer
to analyze bug reports as can be observed in the \jsc\ stacked bar
from Figure~\ref{fig:stacked-engine}.

>>>>

Considering severity levels, it is worth noting that
\jsc{}~\cite{jsc-severity} and \smonkey{}~\cite{mozilla-severity} uses
five levels, whereas \chakra{}~\cite{chakra-severity} and
\veight{}~\cite{v8-severity} use only three. As usual, the smallest
the severity value the highest the severity of the bug. We use a dash
(``-'') in place of the severity level for the cases where the bug
report is pending confirmation. Of the \noBugsTransplantation{} bugs
we reported in this experiment, \noBugsTransplantationConfirmed\ were
promoted from the status ``New'' to ``Confirmed''. Of these, 16 are
severity-2 bugs.  Although we did not find any critical bugs, most of
the bugs are seemingly important as per the categorization given by
engineers. Analyzing the issue tracker of \chakra, we found that
severity-1 bugs are indeed rare. Considering the bug reports confirmed
by developers, \chakra{} was the engine with the highest number--12
(with 3 bugs fixed). Considering the remaining engines, \veight{}
developers confirmed the three bugs we reported, fixing
one. Curiously, Google engineers confirmed the report we issued in a
few hours. Overall, we found that development teams of other engines,
specially \jsc\, took much longer to analyze bug reports as can be
observed in the \jsc\ stacked bar from
Figure~\ref{fig:stacked-engine}. Curiously, however, the bugs that the
\jsc{} team confirms are quickly fixed.
